A Spiking Independent Accumulator Model for Winner-Take-All

### 2017-01-24 doc/paper/paper.tex
Fix italics.

A large body of literature exists examining the optimality of WTA mechanisms and their consistency with neurobiological and psychological data~\cite<e.g.,>{bogacz2006,gold2007,smith2004}.
Here, we investigate the suitability of two different WTA mechanisms in the context of large-scale cognitive modelling.
In particular, we map each mechanism onto a biologically plausible network of spiking neurons, and then compare them using a set of functional benchmarks that are normative in nature.
The first mechanism we consider is an implementation of the {\it leaky, competing accumulator} (LCA) model from~\citeA{usher2001}.
The LCA model has been widely used, for example in versions of the Temporal Context Model~\cite{sederberg2008}, and in work on the Remote Associates Test \todo{not sure this is the right paper} models~\cite<e.g.,>{kajic2017}.
\todo{Add sentence somewhere differentiating our implementation from the latter implementation.  ce: only if it's fairly different}
The second mechanism we consider is the {\it independent accumulator} (IA) model that we propose here, and which involves a secondary thresholding layer that is recurrently connected to a primary integrating layer.

>>>>

A large body of literature exists examining the optimality of WTA mechanisms and their consistency with neurobiological and psychological data~\cite<e.g.,>{bogacz2006,gold2007,smith2004}.
Here, we investigate the suitability of two different WTA mechanisms in the context of large-scale cognitive modelling.
In particular, we map each mechanism onto a biologically plausible network of spiking neurons, and then compare them using a set of functional benchmarks that are normative in nature.
The first mechanism we consider is an implementation of the \emph{leaky, competing accumulator} (LCA) model from~\citeA{usher2001}.
The LCA model has been widely used, for example in versions of the Temporal Context Model~\cite{sederberg2008}, and in work on the Remote Associates Test \todo{not sure this is the right paper} models~\cite<e.g.,>{kajic2017}.
\todo{Add sentence somewhere differentiating our implementation from the latter implementation.  ce: only if it's fairly different}
The second mechanism we consider is the \emph{independent accumulator} (IA) model that we propose here, and which involves a secondary thresholding layer that is recurrently connected to a primary integrating layer.
